\section{Appendix}
\begin{lstlisting}[frame=single,caption=Example of Morfeas\_config.xml,label=lst:Morfeas_config.xml]
<?xml version="1.0" encoding="UTF-8"?>
<!DOCTYPE CONFIG SYSTEM "Morfeas.dtd">
<CONFIG>
  <CONFIGS_DIR>/home/morfeas-test/configuration</CONFIGS_DIR>
  <LOGGERS_DIR>/mnt/ramdisk/Morfeas_Loggers/</LOGGERS_DIR>
  <LOGSTAT_DIR>/mnt/ramdisk/</LOGSTAT_DIR>
  <COMPONENTS>
    <OPC_UA_SERVER>
      <APP_NAME>Default Application</APP_NAME>
    </OPC_UA_SERVER>
    <SDAQ_HANDLER>
      <CANBUS_IF>can0</CANBUS_IF>
    </SDAQ_HANDLER>
    <SDAQ_HANDLER>
      <CANBUS_IF>can1</CANBUS_IF>
    </SDAQ_HANDLER>
	<SDAQ_HANDLER>
      <CANBUS_IF>vcan0</CANBUS_IF>
    </SDAQ_HANDLER>
    <MDAQ_HANDLER>
      <DEV_NAME>LAB_MDAQ</DEV_NAME>
      <IPv4_ADDR>10.0.0.10</IPv4_ADDR>
    </MDAQ_HANDLER>
    <IOBOX_HANDLER>
      <DEV_NAME>LAB_IOBOX</DEV_NAME>
      <IPv4_ADDR>10.0.0.7</IPv4_ADDR>
    </IOBOX_HANDLER>
    <MTI_HANDLER>
      <DEV_NAME>LAB_MTI</DEV_NAME>
      <IPv4_ADDR>10.0.0.11</IPv4_ADDR>
    </MTI_HANDLER>
  </COMPONENTS>
</CONFIG>
\end{lstlisting}
\newpage
\begin{lstlisting}[frame=single,caption=Example of OPC\_UA\_Config.xml,label=lst:OPC_UA_Config.xml]
<?xml version="1.0" encoding="UTF-8"?>
<!DOCTYPE NODESet SYSTEM "Morfeas.dtd">
<NODESet>
  <CHANNEL>
    <ISO_CHANNEL>TE01</ISO_CHANNEL>
    <INTERFACE_TYPE>MDAQ</INTERFACE_TYPE>
    <ANCHOR>167772170.CH1.Val1</ANCHOR>
    <DESCRIPTION>Test for LAB_MDAQ</DESCRIPTION>
    <MIN>-15</MIN>
    <MAX>15</MAX>
    <UNIT>V</UNIT>
  </CHANNEL>
  <CHANNEL>
    <ISO_CHANNEL>TE03</ISO_CHANNEL>
    <INTERFACE_TYPE>MTI</INTERFACE_TYPE>
    <ANCHOR>184549386.ID:4.CH4</ANCHOR>
    <DESCRIPTION>Test for LAB_MTI</DESCRIPTION>
    <MIN>0</MIN>
    <MAX>50</MAX>
    <UNIT>C</UNIT>
  </CHANNEL>
  <CHANNEL>
    <ISO_CHANNEL>TE00</ISO_CHANNEL>
    <INTERFACE_TYPE>SDAQ</INTERFACE_TYPE>
    <ANCHOR>1.CH1</ANCHOR>
    <DESCRIPTION>Test for SDAQ</DESCRIPTION>
    <MIN>-10</MIN>
    <MAX>1000</MAX>
  </CHANNEL>
  <CHANNEL>
    <ISO_CHANNEL>TE02</ISO_CHANNEL>
    <INTERFACE_TYPE>IOBOX</INTERFACE_TYPE>
    <ANCHOR>117440522.RX1.CH2</ANCHOR>
    <DESCRIPTION>Test for LAB_IOBOX RX1 CH2</DESCRIPTION>
    <MIN>-200</MIN>
    <MAX>1200</MAX>
    <UNIT>C</UNIT>
  </CHANNEL>
</NODESet>
\end{lstlisting}
\newpage
\begin{tree_box}[label=tree:OPC_UA_nodeset, title=Morfeas OPC-UA Nodeset]
\dirtree{%
	.1 /.
		.2 ISO\_Channels.
			.3 (..).
		.2 Interfaces.
			.3 IOBOX-ifs.
			.3 MDAQ-ifs.
			.3 SDAQ-ifs.
			.3 MTI-ifs.
		.2 RPI\_Health\_status.
			.3 CPU\_Util(\%).
			.3 CPU\_Temp(°F).
			.3 Disk\_Util(\%).
			.3 RAM\_Util(\%).
}
\end{tree_box}
\begin{tree_box}[title=OPC-UA nodeset for IOBOX-ifs]
	\dirtree{%
		.4 IOBOX-if(*).
			.5 Device\_name.
			.5 IO-BOX Status.
			.5 IO-BOX Status value.
			.5 IPv4 Address.
			.5 I-Link Power Supply.
				.6 Power Supply Vin(V).
				.6 CH(1..4).
					.7 Iout(A).
					.7 Vout(V).
			.5 Receivers.
				.6 RX(1..4).
					.7 CH(1..16).
						.8 Status.
						.8 Status\_value.
						.8 Value.
					.7 Index.
					.7 RX\_Status.
					.7 RX\_success.
	}
\end{tree_box}
\begin{tree_box}[title=OPC-UA nodeset for MDAQ-ifs]
	\dirtree{%
		.4 MDAQ-if(*).
			.5 Device Name.
			.5 IPv4 Address.
			.5 Index.
			.5 MDAQ Status.
			.5 MDAQ Status value.
			.5 Board Temperature(°C).
			.5 Channels.
				.6 (CH1..8).
					.7 Value1..3.
						.8 Measurement.
						.8 Status.
						.8 Status value.
	}
\end{tree_box}
\begin{tree_box}[title=OPC-UA nodeset for SDAQ-ifs]
	\dirtree{%
		.4 SDAQ-if(*).
			.5 Bus\_Util(\%).
			.5 Dev\_on\_Bus.
			.5 Electrics\DTcomment{Only if Morfeas\_RPI\_hat is detected and calibrated}.
				.6 Amperage(A).
				.6 Voltage(V).
				.6 Shunt Temp(°F).
			.5 SDAQnet.
				.6 SDAQ-*(\#\#).
					.7 Address.
					.7 Connected on Bus.
					.7 S/N.
					.7 TimeDiff.
					.7 Info.
						.8 Channels on SDAQ.
						.8 Firm\_rev.
						.8 HW\_rev.
						.8 Max\_cal\_points.
						.8 Samplerate.
						.8 Type.
					.7 Status.
						.8 Error.
						.8 Mode.
						.8 Status.
						.8 inSync.
					.7 Channels.
						.8 CH1..n.
							.9 Calibration Date.
							.9 Calibration Points.
							.9 Period (Months).
							.9 Status.
							.9 Status value.
							.9 Timestamp.
							.9 Unit.
							.9 Value.
	}
\end{tree_box}
\newpage
\begin{tree_box}[title=OPC-UA nodeset for MTI-ifs]
	\dirtree{%
		.4 MTI-if(*).
			.5 Device Name.
			.5 IPv4 Address.
			.5 MTI Status.
			.5 MTI Status value.
			.5 MTI Health.
				.6 Battery Capacity(\%).
				.6 Battery Voltage(V).
				.6 Battery Status(\%).
				.6 CPU Temperature(°C).
			.5 Radio.
				.6 Data rate.
				.6 RF Channel.
				.6 Tele Dev type.
				.6 new\_MTI\_config()\DTcomment{Method to control the radio mode}.
				.6 Tele(***)\DTcomment{Contents depends at radio mode}.
	}
\end{tree_box}
\begin{tree_box}[title=OPC-UA nodeset MTI's Tele object at TC mode]
	\dirtree{%
		.1 Tele(TC\#).
			.2 Packet Index.
			.2 RX Success ratio(\%).
			.2 RX Status.
			.2 Sample to Fail.
			.2 Samples to Validate.
			.2 isValid.
			.2 CH(1..N).\DTcomment{N=amount of inputs}.
				.3 Status.
				.3 Status Value.
				.3 Value.
	}
\end{tree_box}
\begin{tree_box}[title=OPC-UA nodeset MTI's Tele object at QUAD mode]
	\dirtree{%
		.1 Tele(QUAD).
			.2 Packet Index.
			.2 RX Success ratio(\%).
			.2 RX Status.
			.2 isValid.
			.2 CH1..2.
				.3 Raw Counter
				.3 Status.
				.3 Status Value.
				.3 Value.
				.3 Pulse Gen.
					.4 Max.
					.4 Min.
					.4 Saturate.
					.4 Scale.
					.4 new\_Gen\_config()\DTcomment{Method to configure PWM Gens}.
	}
\end{tree_box}
\newpage
\begin{tree_box}[title=OPC-UA nodeset MTI's Tele object at RMSW/MUX mode, label=tree:RMSW/MUX]
	\dirtree{%
		.6 Tele(RMSW/MUX).
			.7 Amount of Devices.
			.7 Global Controls.
				.8 Global ON/OFF Control.
				.8 Global ON/OFF state.
				.8 Global Sleep Control.
				.8 Global Sleep state.
				.8 MTI\_Global\_SWs()\DTcomment{Method to configure the controls}.
			.7 MUX(ID:\#).
				.8 Device temp(°C).
				.8 ID.
				.8 Last RX(sec).
				.8 Memory Offset.
				.8 Supply Voltage(V).
				.8 Type.
				.8 Controls.
					.9 CH(1..4)\_state.
					.9 TX Rate(sec).
					.9 ctrl\_tele\_SWs()\DTcomment{Method to control the Multiplexers}.
			.7 Mini\_RMSW(ID:\#).
				.8 Device temp(°C).
				.8 ID.
				.8 Last RX(sec).
				.8 Memory Offset.
				.8 Supply Voltage(V).
				.8 Type.
				.8 CH(1..4).
					.9 Measurement.
					.9 Status.
					.9 Status value.
				.8 Controls.
					.9 Main Switch.
					.9 TX Rate(sec).
					.9 ctrl\_tele\_SWs()\DTcomment{Method to control the Main switch}.
			.7 RMSW(ID:\#).
				.8 Device temp(°C).
				.8 ID.
				.8 Last RX(sec).
				.8 Memory Offset.
				.8 Supply Voltage(V).
				.8 Type.
				.8 Controls.
					.9 CH(1..2)\_state.
					.9 Main switch.
					.9 TX Rate(sec).
					.9 ctrl\_tele\_SWs()\DTcomment{Method to control the Switches}.
				.8 CH(1..2).
					.9 CH\# Amperage(A).
					.9 CH\# Voltage(V).
	}
\end{tree_box}